A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-10-18 doc/large_strain.tex
minor

D.~Davydov acknowledge the financial support of the German Research Foundation (DFG), grant DA 1664/2-1
and the Competence Network for Technical and Scientific High Performance Computing in Bavaria (KONWIHR).

>>>>

D.~Davydov acknowledge the financial support of the German Research Foundation (DFG), grant DA 1664/2-1.
